### 2020-01-30 wuhan.tex
Rewrite Discussion; nothing added

Estimating the basic reproductive number $\mathcal R_0$ is crucial for predicting the course of an outbreak and planning intervention strategies.
Here, we evaluated the statistical validity of the estimates of $\mathcal R_0$ for the novel coronavirus outbreak using a novel statistical framework, based on the gamma approximation of the generation-interval distribution \citep{park2019practical}.
Our results demonstrate the importance of accounting for uncertainties associated with the underlying generation-interval distributions, especially with the amount of dispersion in the generation intervals:
assuming a narrow generation-interval distribution can make the estimate of $\mathcal R_0$ too sensitive to the estimates of the exponential growth rate $r$.

Narrow confidence intervals associated with early estimates of $\mathcal R_0$ partly depend on the statistical approches that the estimates rely on.
Of the six studies that we reviewed, two of them directly fit their models to cumulative number of confirmed cases.
Although the formula for the cumulative curve (e.g., logistic model) is much simpler and familiar to many people, 
fitting a model to cumulative number of cases can bias the parameter estimate and give overly narrow confidence intervals as it violates the ``independence of error'' assumption \citep{ma2014estimating, king2015avoidable}.
We emphasize that all models should be fitted to raw incidence data for any future analyses.

Concluding paragraph with a message?

>>>>

Estimating the basic reproductive number $\mathcal R_0$ is crucial for predicting the course of an outbreak and planning intervention strategies.
Here, we used a simple framework \citep{park2019practical} to compare  estimates of $\mathcal R_0$ for the novel coronavirus outbreak.
Our results demonstrate the importance of accounting for uncertainties associated with the underlying generation-interval distributions, including with the amount of dispersion in the generation intervals:
although our pooled estimates are relatively insensitive to the estimated uncertainty, our analysis of individual studies shows that assuming too narrow a generation-interval distribution can make the estimate of $\mathcal R_0$ too sensitive to the estimates of the exponential growth rate $r$.

Narrow confidence intervals associated with early estimates of $\mathcal R_0$ partly depend on the statistical approches used to estimate the exponential growth rate $r$.
Of the six studies that we reviewed, two of them directly fit their models to cumulative number of confirmed cases.
Although the formula for the cumulative curve (e.g., logistic model) is much simpler and familiar to many people, fitting a model to cumulative number of without accounting for problems with the dependent error structure can both bias parameter narrow confidence intervals \citep{ma2014estimating, king2015avoidable}.
Naive fits to cumulative incidence data should be avoided.
